Fast solvers for the high-order FEM simplicial de Rham complex \thanks{Submitted to the editors July XX, 2024. \funding{ PDB and PEF were supported by EPSRC grant EP/W026260/1. } }

### 2024-06-18 paper/paper.tex
Sketch for the introduction

>>>>

Main challenges, motivations
\begin{itemize}
\item In high-order FEM, the curse of dimensionality affects operator
   evaluation and relaxation methods in multigrid and domain-decomposition.  
\item For tensor product cells,
   a tensor product basis will expose the structure to decouple the
   multidimensional problems into a sequence of one-dimensional problems.
   Sum-factorization enables fast operator evaluation, and the fast
   diagonalization method addresses the efficient solution of problems
   structured subdomains.  On unstructured subdomains, an optimal strategy
   using static condensation with FDM bases was proposed in our previous
   work.
\item For simplices, Bernstein--Bezier expansions enable sum-factorized
   operator evaluation, but there is no knowledge of basis transformation
   that can diagonalize a problem on any structured or unstructured subdomain.
\end{itemize}

Other approaches
\begin{itemize}
\item Low-order-refined preconditioning, not fully understood/far from optimal.
\item Sparse hierarchical bases from Beuchler \& Schoberl constructed from integrated Jacobi polynomials. 
   These bases still couple interior DOFs, making static condensation difficult.
\end{itemize}

Our approach, main solver design ingredients:
\begin{itemize}
\item Construction of degrees of freedom that promote sparsity in the reference element, 
   which in turn increases the efficiency of block preconditioners/decoupling strategies. The key idea is
      to use the degrees of freedom proposed by Demkowicz with eigenbases for the space of bubbles on each subentity.
\item Construction of space decompositions around small subdomains constructed around vertices and edges.
\end{itemize}
